---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidydlnm

<!-- badges: start -->
<!-- badges: end -->

The goal of tidydlnm is to make outputs from the package [`dlnm`](https://github.com/gasparrini/dlnm) more tidyverse-friendly.

**Note: Only DLMs are currently supported. DLNM support coming soon.**

## Installation

You can install tidydlnm from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("geomarker-io/tidydlnm")
```
## Example

Suppose we have the following data, where lags 0 through 9 are the values of some exposure experienced 0 to 9 days before the outcome `y`.

```{r, echo = F, message = F}
library(tidyverse)
set.seed(212)
d <- data.frame(rnorm(n=100, mean=0.3, sd=1))
names(d) <- c("lag0")
d <- d %>%
    as_tibble() %>%
    mutate(lag1 = rnorm(n=100, mean=lag0, sd=1),
           lag2 = rnorm(n=100, mean=lag1, sd=1),
           lag3 = rnorm(n=100, mean=lag2, sd=1),
           lag4 = rnorm(n=100, mean=lag3, sd=1),
           lag5 = rnorm(n=100, mean=lag4, sd=1),
           lag6 = rnorm(n=100, mean=lag5, sd=1),
           lag7 = rnorm(n=100, mean=lag6, sd=1),
           lag8 = rnorm(n=100, mean=lag7, sd=1),
           lag9 = rnorm(n=100, mean=lag8, sd=1))

d <- d %>%
    mutate(y = rnorm(100, mean = 53.5 + 2*(lag3+lag4), sd=10))

d
```


First, use the `dlnm` package to fit a distributed lag model. We create the crossbasis, fit the model, and create the crosspred object. (For more info, see [https://github.com/gasparrini/dlnm](https://github.com/gasparrini/dlnm)). 

```{r, message = F}
library(dlnm)
Q <- select(d, lag0:lag9)

cb <- crossbasis(Q, lag=9,
                   argvar=list("lin"),
                   arglag=list(fun="ns"))
mod <- lm(y ~ cb, data=d)
cpred <- crosspred(cb, mod, at=1, cumul = TRUE)
```

Then use `tidydlnm` to obtain more tidyverse-friendly output and plots, including 

- the estimates at each lag

```{r}
library(tidydlnm)

lag_fits <- tidy_lag_fits(cpred)
tidy_lag_plot(lag_fits)
```

- the estimated effect over all lags

```{r}
tidy_overall_fit(cpred)
```

- cumulative effect estimates at each lag

```{r}
cumul_fits <- tidy_cumul_fits(cpred)
```

Note that the same plotting function can be used to plot the cumulative estimates. Also, since this is a ggplot object, the plot can be customized as any other ggplot. 

```{r}
tidy_lag_plot(cumul_fits) +
  ylab("Estimate") +
  theme_minimal()
```

For a summary of specific windows of association identified by the model, use `tidy_window_summary()`.
```{r}
tidy_window_summary(lag_fits)
```

